An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-05-30 Article/EconGrowth2.Rnw
Added "that".

In this paper, we assess three prominent energy-augmented production functions 
appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
describe each.

>>>>

In this paper, we assess three prominent energy-augmented production functions 
that appear in the literature: Cobb-Douglas (CDe), Constant Elasticity of 
Substitution (CESe), and LINear EXponential (LINEX). The following subsections 
describe each.
